---
title: "EDA"
format: html
editor: visual
---

# Modeling
## Data Cleanup
```{r}
library(randomForest)
library(dplyr)
library(lubridate)
# Load
tx_97 <- read.csv("MavenMarket_Transactions_1997.csv")
tx_98 <- read.csv("MavenMarket_Transactions_1998.csv")
returns <- read.csv("MavenMarket_Returns_1997-1998.csv")
products <- read.csv("MavenMarket_Products.csv")
stores <- read.csv("MavenMarket_Stores.csv")
regions <- read.csv("MavenMarket_Regions.csv")
customers <- read.csv("MavenMarket_Customers.csv")

# Combine tx
transactions <- bind_rows(tx_97, tx_98) %>%
  mutate(transaction_date = mdy(transaction_date),
         key = paste(product_id, store_id))

# returns key
returns <- returns %>%
  mutate(return_date = mdy(return_date),
         key = paste(product_id, store_id))

# left join key
returns_short <- returns %>% select(key, return_date)
transactions <- left_join(transactions, returns_short, by = "key")

# label returns
transactions <- transactions %>%
  mutate(
    Returned = ifelse(!is.na(return_date), 1, 0)
  ) %>%
  select(-return_date, -key)

# Make final dataset
transactions <- transactions %>%
  left_join(products, by = "product_id") %>%
  left_join(stores, by = "store_id") %>%
  left_join(regions, by = "region_id") %>%
  left_join(customers, by = "customer_id")

# Feature engineering. We want to create a variable for season, profit margin, and store age.
transactions <- transactions %>%
  mutate(
    season = quarter(transaction_date),
    profit_margin = product_retail_price - product_cost,
    store_age = as.numeric(difftime(transaction_date, mdy(first_opened_date), units = "days"))
  )

# Final model dataset
model_data <- transactions %>%
  select(
    Returned, quantity, season, product_brand, product_retail_price, product_cost, profit_margin, product_weight, store_type, total_sqft, grocery_sqft, sales_district, sales_region, store_age, gender, marital_status, yearly_income, total_children, num_children_at_home, education, homeowner
  ) %>%
  na.omit()


```

## Training Validation Test sets
```{r}

# Convert character columns to factors
model_data <- mutate_if(model_data, is.character, as.factor)
model_data <- model_data %>% 
  mutate(
    Returned = as.factor(Returned),
    season = as.factor(season),
    total_children = as.factor(total_children),
    num_children_at_home = as.factor(num_children_at_home)
  )

# frequency of each brand
brand_counts <- table(model_data$product_brand)
# RF only handles up to 50 categories, let's select top 50
top_brands <- names(sort(brand_counts, decreasing = TRUE))[1:50]

# keep top brands, label the rest as "Other"
model_data <- model_data %>%
  mutate(product_brand = ifelse(product_brand %in% top_brands, as.character(product_brand), "Other")) %>%
  mutate(product_brand = as.factor(product_brand))

# First split: 70% training, 30% remaining
set.seed(123)
sample_index <- sample(1:nrow(model_data), size = 0.7 * nrow(model_data))
train_data <- model_data[sample_index, ]
remaining_data <- model_data[-sample_index, ]

# Second split: Divide the remaining 30% equally into validation and test sets (15% each)
set.seed(123)
val_index <- sample(1:nrow(remaining_data), size = 0.5 * nrow(remaining_data))
validation_data <- remaining_data[val_index, ]
test_data <- remaining_data[-val_index, ]
```

## models
### Bagging Model
```{r}
library(randomForest)
# BAGGING MODEL
bag_model <- randomForest(Returned ~ ., data=train_data, mtry = ncol(train_data) - 1, importance=T, na.action=na.omit)

```
#### Validation set
```{r}
# Evaluate on the validation set
bag_val_preds <- predict(bag_model, validation_data)
bag_val_conf <- table(validation_data$Returned, bag_val_preds)
bag_val_error <- 1 - sum(diag(bag_val_conf)) / sum(bag_val_conf)

print("Bagging Validation Confusion Matrix:")
print(bag_val_conf)
print(paste("Bagging Validation Error Rate:", round(bag_val_error, 4)))
```

##### Confusion Matrix (Validation)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(bag_val_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- bag_val_conf["1", "1"]  # True Positives
fp <- bag_val_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "Bagging Model — Validation Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- bag_val_conf["1", "1"]
fn <- bag_val_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "Bagging Model — Validation Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

#### Test Set
```{r}
bag_test_preds <- predict(bag_model, test_data)
bag_test_conf <- table(test_data$Returned, bag_test_preds)
bag_test_error <- 1 - sum(diag(bag_test_conf)) / sum(bag_test_conf)

print("Bagging Test Confusion Matrix:")
print(bag_test_conf)
print(paste("Bagging Test Error Rate:", round(bag_test_error, 4)))
```

##### Confusion Matrix (Test)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(bag_test_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- bag_test_conf["1", "1"]  # True Positives
fp <- bag_test_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "Bagging Model — Tesst Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- bag_test_conf["1", "1"]
fn <- bag_test_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "Bagging Model — Test Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```


### Random Forest Model
```{r}
# RANDOM FOREST MODEL
rf_model <- randomForest(Returned ~ ., data=train_data, importance=T, na.action=na.omit)
```

#### Validation Set
```{r}
# Evaluate on the validation set
rf_val_preds <- predict(rf_model, validation_data)
rf_val_conf <- table(validation_data$Returned, rf_val_preds)
rf_val_error <- 1 - sum(diag(rf_val_conf)) / sum(rf_val_conf)

print("Random Forest Validation Confusion Matrix:")
print(rf_val_conf)
print(paste("Random Forest Validation Error Rate:", round(rf_val_error, 4)))
```
##### Confusion Matrix (Validation)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(rf_val_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- rf_val_conf["1", "1"]  # True Positives
fp <- rf_val_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "RF Model — Validation Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- rf_val_conf["1", "1"]
fn <- rf_val_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "RF Model — Validation Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

#### Test Set
```{r}
# FINAL EVALUATION on Test Set
## Evaluate RF on the test set
rf_test_preds <- predict(rf_model, test_data)
rf_test_conf <- table(test_data$Returned, rf_test_preds)
rf_test_error <- 1 - sum(diag(rf_test_conf)) / sum(rf_test_conf)
print("Random Forest Test Confusion Matrix:")
print(rf_test_conf)
print(paste("RF Test Error Rate:", round(rf_test_error, 4)))

## Evaluate Random Forest on the test set
rf_test_preds <- predict(rf_model, test_data)
rf_test_conf <- table(test_data$Returned, rf_test_preds)
rf_test_error <- 1 - sum(diag(rf_test_conf)) / sum(rf_test_conf)
print("Random Forest Test Confusion Matrix:")
print(rf_test_conf)
print(paste("Random Forest Test Error Rate:", round(rf_test_error, 4)))
```

##### Confusion Matrix (Test)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(rf_test_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- rf_test_conf["1", "1"]  # True Positives
fp <- rf_test_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "RF Model — Test Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- rf_test_conf["1", "1"]
fn <- rf_test_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "RF Model — Test Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

## Variable Importance Charts
```{r}
# Plot with adjusted margin and fewer variables
par(mar = c(5, 10, 4, 2))  # Bottom, Left, Top, Right margins

# Show top 15 most important variables only
varImpPlot(bag_model, n.var = 15, main = "Variable Importance (Bagging Model)")

# Show top 15 most important variables only
varImpPlot(rf_model, n.var = 15, main = "Variable Importance (RF Model)")
```


# Clean up data after Var Imp Chart
```{r}

# keep top brands, label the rest as "Other"

model_data_revised <- model_data %>%
  select(Returned, product_brand, sales_district, profit_margin, product_weight, product_cost, store_age, product_retail_price, product_weight, yearly_income)


# First split: 70% training, 30% remaining
set.seed(123)
sample_index <- sample(1:nrow(model_data_revised), size = 0.7 * nrow(model_data_revised))
train_data <- model_data_revised[sample_index, ]
remaining_data <- model_data_revised[-sample_index, ]

# Second split: Divide the remaining 30% equally into validation and test sets (15% each)
set.seed(123)
val_index <- sample(1:nrow(remaining_data), size = 0.5 * nrow(remaining_data))
validation_data <- remaining_data[val_index, ]
test_data <- remaining_data[-val_index, ]
```

```{r}
# BAGGING MODEL
bag_model <- randomForest(Returned ~ ., data=train_data, mtry = ncol(train_data) - 1, importance=T, na.action=na.omit)
```

#### Validation set
```{r}
# Evaluate on the validation set
bag_val_preds <- predict(bag_model, validation_data)
bag_val_conf <- table(validation_data$Returned, bag_val_preds)
bag_val_error <- 1 - sum(diag(bag_val_conf)) / sum(bag_val_conf)

print("Bagging Validation Confusion Matrix:")
print(bag_val_conf)
print(paste("Bagging Validation Error Rate:", round(bag_val_error, 4)))
```

##### Confusion Matrix (Validation)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(bag_val_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- bag_val_conf["1", "1"]  # True Positives
fp <- bag_val_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "Bagging Model — Validation Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- bag_val_conf["1", "1"]
fn <- bag_val_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "Bagging Model — Validation Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

#### Test Set
```{r}
bag_test_preds <- predict(bag_model, test_data)
bag_test_conf <- table(test_data$Returned, bag_test_preds)
bag_test_error <- 1 - sum(diag(bag_test_conf)) / sum(bag_test_conf)

print("Bagging Test Confusion Matrix:")
print(bag_test_conf)
print(paste("Bagging Test Error Rate:", round(bag_test_error, 4)))
```

##### Confusion Matrix (Test)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(bag_test_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- bag_test_conf["1", "1"]  # True Positives
fp <- bag_test_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "Bagging Model — Test Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- bag_test_conf["1", "1"]
fn <- bag_test_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "Bagging Model — Test Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

### Random Forest Model
```{r}
# RANDOM FOREST MODEL
rf_model <- randomForest(Returned ~ ., data=train_data, importance=T, na.action=na.omit)
```

#### Validation Set
```{r}
# Evaluate on the validation set
rf_val_preds <- predict(rf_model, validation_data)
rf_val_conf <- table(validation_data$Returned, rf_val_preds)
rf_val_error <- 1 - sum(diag(rf_val_conf)) / sum(rf_val_conf)

print("Random Forest Validation Confusion Matrix:")
print(rf_val_conf)
print(paste("Random Forest Validation Error Rate:", round(rf_val_error, 4)))
```
##### Confusion Matrix (Validation)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(rf_val_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- rf_val_conf["1", "1"]  # True Positives
fp <- rf_val_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "RF Model — Validation Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- rf_val_conf["1", "1"]
fn <- rf_val_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "RF Model — Validation Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

#### Test Set
```{r}
# FINAL EVALUATION on Test Set
## Evaluate RF on the test set
rf_test_preds <- predict(rf_model, test_data)
rf_test_conf <- table(test_data$Returned, rf_test_preds)
rf_test_error <- 1 - sum(diag(rf_test_conf)) / sum(rf_test_conf)
print("Random Forest Test Confusion Matrix:")
print(rf_test_conf)
print(paste("RF Test Error Rate:", round(rf_test_error, 4)))

## Evaluate Random Forest on the test set
rf_test_preds <- predict(rf_model, test_data)
rf_test_conf <- table(test_data$Returned, rf_test_preds)
rf_test_error <- 1 - sum(diag(rf_test_conf)) / sum(rf_test_conf)
print("Random Forest Test Confusion Matrix:")
print(rf_test_conf)
print(paste("Random Forest Test Error Rate:", round(rf_test_error, 4)))
```

##### Confusion Matrix (Test)
```{r}
library(ggplot2)
library(reshape2)

# Convert confusion matrix to dataframe
conf_df <- as.data.frame(rf_test_conf)
colnames(conf_df) <- c("Actual", "Predicted", "Freq")

# Replace factor levels
conf_df$Actual <- factor(conf_df$Actual, levels = c("0", "1"), labels = c("No Return", "Return"))
conf_df$Predicted <- factor(conf_df$Predicted, levels = c("0", "1"), labels = c("No Return", "Return"))

# Add percentage column
conf_df$Percent <- round(conf_df$Freq / sum(conf_df$Freq) * 100, 1)

# Compute precision
tp <- rf_test_conf["1", "1"]  # True Positives
fp <- rf_test_conf["0", "1"]  # False Positives
precision <- tp / (tp + fp)

# New title
plot_title <- paste0(
  "RF Model — Test Set\n",
  "Confusion Matrix | Precision: ", round(precision * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
##################################################
# Compute sensitivity
tp <- rf_test_conf["1", "1"]
fn <- rf_test_conf["1", "0"]
sensitivity <- tp / (tp + fn)

# Updated title
plot_title <- paste0(
  "RF Model — Test Set\n",
  "Confusion Matrix | Sensitivity: ", round(sensitivity * 100, 2), "%"
)

# Plot
ggplot(conf_df, aes(x = Predicted, y = Actual, fill = Freq)) +
  geom_tile(color = "white") +
  geom_text(aes(label = paste0(Freq, "\n(", Percent, "%)")), size = 5) +
  scale_fill_gradient(low = "lightblue", high = "steelblue") +
  labs(
    title = plot_title,
    x = "Predicted Label",
    y = "Actual Label"
  ) +
  theme_minimal(base_size = 14)
```

